DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-05 ase2017/paper.tex
Fill in the CEGIS section

\textcolor{red}{Cristina: can you please generalize our CEGIS implementation for control here?}

\textcolor{red}{We have to talk about the naive and AA back-ends, which are based on our CEGIS framework}

>>>>

%\textcolor{red}{Cristina: can you please generalize our CEGIS implementation for control here?}

%% The input specification provided to the program synthesizer is of the form
%% $\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
%% (where a function is represented by the program computing it),
%% $a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
%% We~interpret the ground terms over some finite domain~$\mathcal{D}$.

The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors that is updated incrementally.  Given a stability
and safety specification, the inductive synthesis procedure tries to
find a candidate solution satisfying the specification for the given set of test inputs.
%
If the synthesis phase succeeds in finding a witness, this witness is
a candidate solution to the full synthesis formula.  We pass this
candidate solution to the validation phase, which checks whether it is
a full solution (i.e., satisfies the specification for all possible
inputs).  If this is the case, then the algorithm terminates.
Otherwise, additional information is provided to the inductive
synthesis phase in the form of a new counterexample that is added to
the set of test inputs and the loop iterates again.

We use two different instantiations of the synthesiser
in order to synthesise stable and safe digital
controllers. The two approaches differ in
the manner in which they check the safety specification
for all reachable states.

The first approach uses a multi-staged verification process. 
Essentially, it starts by devising a
digital controller that stabilizes the system while remaining safe for a
pre-selected time horizon and a single initial state; then, it
employs a multi-staged verification process:
(i) The first verification stage checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage 
 restores soundness with respect to the plant's precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller $K$,
i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
system such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.

Instead of unfolding the dynamics, the second approach
employs {\em abstract acceleration}~\cite{cattaruzza2015unbounded} to
evaluate all possible progressions of the system simultaneously. 
Additionally, the second approach uses abstraction refinement,
enabling us to always start with a very simple description regardless of the
dynamics complexity, and only expand to more complex models
when a solution cannot be found.

\textcolor{red}{add more for the second approach}

%\textcolor{red}{We have to talk about the naive and AA back-ends, which are based on our CEGIS framework}
